A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
DCT discussion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@950 43ef1190-90fd-4dd7-a769-d0121f02b80e

We next examine the freshness lifetime of the 2965 information
resources that returned a successful response, either with SPARQL
results or RDF data. 405 returned valid headers, but 114 did so to
\emph{prohibit} caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occured, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching.

@@

@@

@@

@@

@@

For all others, we parsed the response, and recorded any errors if the
parser concluded the content were invalid. We noted that the Dublin Core
Metadata terms vocabulary has a number of predicates that may become
useful in determining heuristic freshness in the future, so we
recorded any statements containing the predicates \rdfterm{dct:date},
\rdfterm{dct:accrualPeriodicity}, \rdfterm{dct:created},
\rdfterm{dct:issued}, \rdfterm{dct:modified} or \rdfterm{dct:valid}.

>>>>

We next examine the freshness lifetime of the 2965 information
resources that returned a successful response, either with SPARQL
results or RDF data.

\subsubsection{Standards-compliant caching headers}

Of these resources, 405 returned valid headers, but 114 did so to
\emph{prohibit} caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occured, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching.

@@

\subsubsection{Simple heuristic freshness estimates}

@@

\subsubsection{Heuristic freshness from Dublin Core properties}

We noted that the Dublin Core Metadata terms vocabulary has a number
of predicates that may become useful in determining heuristic
freshness in the future, so we recorded any statements containing the
predicates \rdfterm{dct:date}, \rdfterm{dct:accrualPeriodicity},
\rdfterm{dct:created}, \rdfterm{dct:issued}, \rdfterm{dct:modified} or
\rdfterm{dct:valid}.

First, we compare dates given in \rdfterm{dct:modified} to dates given
in \httph{Last-Modified} when both are available for a resource. They
are often not the same, but it appears that dates in the former are
further back in time than the latter. We speculate that this may be
due to that the webserver tracks semantically insignificant changes
through the filesystem, while authors of RDF only update timestamp
when significant changes are made, or it may be that authors forget to
update their timestamps.

\rdfterm{dct:modified} occurs in 2687 triples, but 2487 of these does
not have the Request-URI of the information resource as their subject,
i.e. it gives the last modification time of some subgraph of the
returned RDF. Nevertheless, given its prevalence, it is highly likely
that the presence of \rdfterm{dct:modified} will be useful in
determining a heuristic freshness lifetime, as the latest date may be
used.\todo{Actually calculate lifetimes based on this and compare}

\rdfterm{dct:valid} occurred 21 times, and could be used in lieu of an
\httph{Expires} header, but none of these occurences had a date in the
future.

\rdfterm{dct:accrualPeriodicity} occurred only twice, and in neither
case contained machine readable data.

\rdfterm{dct:date}, \rdfterm{dct:created} and \rdfterm{dct:issued}
were present in 36, 389 and 1475 triples respectively. They correspond
roughly to the \httph{Date} header, which is present in all requests,
and they are therefore not important, but given their prevalence they
could be useful in further analysis.

@@

Further investigate the correctness of the \rdfterm{dct:modified} property.

@@

A change periodicity predicate should be standardized in Void.

@@

For all others, we parsed the response, and recorded any errors if the
parser concluded the content were invalid.
